`SCPCL001114` - Exploration of gene set based methods for tumor cell assignment

### 2024-07-16 analyses/cell-type-ewings/exploratory_analysis/annotation_notebooks/SCPCS000752/SCPCL001114_tumor-gene-expression-exploration.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

In this notebook we attempt to identify tumor cells in `SCPCL001114` using the following orthogonal marker gene based methods:

@@

# compare using a confusion matrix
caret::confusionMatrix(
    table(
      classification_df$marker_gene_classification, 
      classification_df$ref_marker_gene_classification)
  ) 
```

>>>>

In this notebook we attempt to identify tumor cells in `SCPCL001114` using the following marker gene based methods:

@@

# compare using a confusion matrix
caret::confusionMatrix(
    table(
      classification_df$ref_marker_gene_classification,
      classification_df$marker_gene_classification)
  ) 
```
